Comparing Two Approaches for Solving Constrained Global Optimization Problems

### 2017-10-06 2017/LION_Barkalov_Lebedev/LION2017_BarkalovLebedev.tex
Some references have been corrected

The experiments was carried out with the use of GKLS generator.  This generator for the functions of arbitrary dimensionality with known properties (the number of local minima, the size of their domains of attraction, the global minimizer, etc.) has been proposed in \cite{Gaviano}. Eight GKLS classes of differentiable test functions of the dimensions $N = 2, 3, 4,$ and 5, have been used. For each dimension, both \textit{Hard} and \textit{Simple} classes have been considered. The difficulty of a class was increased either by decreasing the radius of the attraction region of the global minimizer, or by decreasing the distance from the global minimizer $y^\ast$ to the domain boundaries. Application of this generator for studying some unconstrained optimization algorithms has been described in \cite{Kvasov2006}--\cite{SergeyevKvasov2015}.

@@

\bibitem{GergelLION} 
Gergel, V.: An Approach for Generating Test Problems of Constrained Global Optimization. Proceedings of the LION11 conference (2017) [submitted]

>>>>

The experiments was carried out with the use of GKLS generator.  This generator for the functions of arbitrary dimensionality with known properties (the number of local minima, the size of their domains of attraction, the global minimizer, etc.) has been proposed in \cite{Gaviano}. Eight GKLS classes of differentiable test functions of the dimensions $N = 2, 3, 4,$ and 5, have been used. For each dimension, both \textit{Hard} and \textit{Simple} classes have been considered. The difficulty of a class was increased either by decreasing the radius of the attraction region of the global minimizer, or by decreasing the distance from the global minimizer $y^\ast$ to the domain boundaries. Application of this generator for studying some unconstrained optimization algorithms has been described in \cite{Grishagin2016}, \cite{Kvasov2006}--\cite{SergeyevKvasov2015}.

@@

\bibitem{GergelLION} 
Gergel, V.: An approach for generating test problems of constrained global optimization. In: Battiti, R., Kvasov, D., Sergeyev, Y. (eds.) LION 2017. LNCS, vol. 10556. Springer (2017) DOI:10.1007/978-3-319-69404-7\_24
